Recruiting Chapter

### 2020-11-20 manuscript.Rmd
meh

WHICH TABLES/FIGURES IN THIS SECTION

- one-mode plot w/ vertices colored by cluster
  - probably better to show all or pub out-state but not both
  - given the focus is which public universities behave like private universities, think there is rationale for restricting public university events to out-of-state because out-of-state visits are behavior associated w/ privatization; also this makes it slightly different than what has already been analyzed
- show ego figure organized by cluster
  - make this one only include out-of-state events for public research universities
- maybe which schools most visited?

WHAT SHOULD FOCUS OF RESULTS BE

- which public universities behave like private universities
  - this strikes me as the case for out-of-state only

```{r, include = FALSE, eval = FALSE}
#df <- readRDS('./assets/tables/table_ego_all.RDS')
df <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
df %>% glimpse()
df %>% select(ID,University,Cluster,total) %>% 
  arrange(Cluster,total) %>% print(n=50)
```

>>>>

# Summary and Discussion

[ADD SUCCINCT, CONCRETE SUMMARY FOCUSING ON BIG FINDINGS AND THEMES; VERY BRIEF DISCUSSION]
